API design for machine learning software: experiences from the scikit-learn project

### 2013-10-18 paper.tex
Define some accronyms.
Also, SGD is not a linear model but an optimization method.

Estimator initialization and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of named hyper-parameter values
(e.g., the $C$ constant in SVMs)
and can be considered a function
that maps these values to actual learning algorithms.
The constructor does not see any actual data.
All it does is attach the given parameters to the object.
For the sake of model inspection, hyper-parameters are set as public attributes,
which is especially important in model selection settings.
Default hyper-parameter values are provided for all built-in estimators.
These defaults are set to be relevant in many common
situations in order to make estimators effective \textit{out-of-box}.

@@

param_grid = [
  {"kernel": ["linear"], "C": [1, 10, 100, 1000]},
  {"kernel": ["rbf"], "C": [1, 10, 100, 1000],
   "gamma": [0.001, 0.0001]}
]
clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
\end{pythoncode}
\caption{Optimizing the hyper-parameters of an SVM for $F_1$ score.}
\label{svm-gridsearch}
\end{figure*}

@@

Finally, the Gensim topic modeling toolkit \citep{rehurek2010gensim}
exemplifies an API geared toward ``big data'' processing.
Gensim's method of dealing with large datasets is to use algorithms
that have small space complexity and can be updated online.
The API is designed around the Python concept of an ``iterable''
(supported in the language by a restricted form of co-routines called generators).
Some \sklearn estimators, notably Naïve Bayes and linear model SGD,\footnote{
  Least-squares, logistic regression and SVM models.}
have a \texttt{partial\_fit} method to learn from a stream of samples
that is divided into mini-batches (chunks).
This way of processing, as argued in Section~\ref{sec:arrays},
allows for more efficient implementation.
We make no attempt to hide this batch-oriented processing from the user,
allowing control over the amount of memory dedicated to \sklearn algorithms.

>>>>

Estimator initialization and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of named hyper-parameter values
(e.g., the $C$ constant in Support Vector Machines (SVM))
and can be considered a function
that maps these values to actual learning algorithms.
The constructor does not see any actual data.
All it does is attach the given parameters to the object.
For the sake of model inspection, hyper-parameters are set as public attributes,
which is especially important in model selection settings.
Default hyper-parameter values are provided for all built-in estimators.
These defaults are set to be relevant in many common
situations in order to make estimators effective \textit{out-of-box}.

@@

param_grid = [
  {"kernel": ["linear"], "C": [1, 10, 100, 1000]},
  {"kernel": ["rbf"], "C": [1, 10, 100, 1000],
   "gamma": [0.001, 0.0001]}
]
clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
\end{pythoncode}
\caption{Optimizing the hyper-parameters of a Support Vector Machine for $F_1$
score.}
\label{svm-gridsearch}
\end{figure*}

@@

Finally, the Gensim topic modeling toolkit \citep{rehurek2010gensim}
exemplifies an API geared toward ``big data'' processing.
Gensim's method of dealing with large datasets is to use algorithms
that have small space complexity and can be updated online.
The API is designed around the Python concept of an ``iterable''
(supported in the language by a restricted form of co-routines called generators).
Some \sklearn estimators, notably Naïve Bayes and Stochastic Gradient Descent
(for learning linear models such as
logistic regression and SVM),
have a \texttt{partial\_fit} method to learn from a stream of samples
that is divided into mini-batches (chunks).
This way of processing, as argued in Section~\ref{sec:arrays},
allows for more efficient implementation.
We make no attempt to hide this batch-oriented processing from the user,
allowing control over the amount of memory dedicated to \sklearn algorithms.
